Fast solvers for the high-order FEM simplicial de Rham complex \thanks{Submitted to the editors July XX, 2024. \funding{ PDB and PEF were supported by EPSRC grant EP/W026260/1. } }

### 2024-06-14 paper/paper.tex
Notation for bubbles

We follow the definition of interpolation degrees of freedom from \cite{demkowicz00}
to construct dual bases that promote orthgonality in the $\Ltwo(\Khat)$ and $H(\mathrm{d}, \Khat)$ inner
products.

@@

Let $\Delta^d$ be the equilateral $d$-simplex.
We define a basis for the dual of $\CG_p$ as 
point evaluations at $V \in \text{vertices}(\Delta^d)$,
\begin{equation}
   \ell^V(v) = v(\bx_V),
\end{equation}
and for each sub-entity $S \in \text{edges}(\Delta^d) \cup \text{faces}(\Delta^d) \cup \text{interior}(\Delta^d)$
we take integral moments of surface gradients, 
\begin{equation}
   \ell^S_j(v) = (\grad_S\phi^S_j, \grad_S v)_{S},
\end{equation}
where $\grad_S$ is the tangential gradient on $S$,
and $\{\phi^S_j\}$ is a basis for
$\P_{p,0}(S) = \{ v \in \P_p(S): v = 0 \text{ on } \partial S \}$, such that
\begin{equation} \label{eq:hgrad-fdm}
   (\grad_S\phi^S_j, \grad_S\phi^S_i)_{S} = \delta_{ij}, \quad
   (\phi^S_j, \phi^S_i)_{S} = \lambda_j\delta_{ij}.
\end{equation}
The eigenbases $\{\phi^S_j\}$ are numerically computed offline and only once 
on the reference interval, triangle, and tetrahedron.

@@

We define a basis for the dual of $V^1_{p, p_E}(K)$ as 
tangential moments along $E\in \text{edges}(\Delta^d)$,
\begin{equation}
   \ell^E_j(v) = (q_j, v\cdot \bt)_E, \quad q_j \in \P_{p_E}(E), 
\end{equation}
and for each sub-entity $S \in \text{faces}(\Delta^d) \cup \text{interior}(\Delta^d)$,
\begin{align}
   \ell^{S,0}_j(v) &= (\grad_S\phi^S_j, v)_{S}, \\
   \ell^{S,1}_j(v) &= (\curl_S\Phi^S_j, \curl_S v)_{S},
\end{align}
where $\curl_S$ is the tangential curl on $S$,
$\{\phi^S_j\}$ are the $H_0(\grad, S)$ bases constructed in \eqref{eq:hgrad-fdm},
and $\{\curl_S\Phi^S_j\}$ is a basis for $\curl_S \mathbb{X}_{p_S}(S)$,
$\mathbb{X}_{p_S}(S) = [\P_{p_S}(S)]^d \cap H_0(\curl, S)$, such that
\begin{equation} \label{eq:hcurl-fdm}
   (\curl_S\Phi^S_j, \curl_S\Phi^S_i)_{S} = \delta_{ij}, \quad
   (\Phi^S_j, \Phi^S_i)_{S} = \lambda_j\delta_{ij}, \quad
   \Phi^S_j\times\bn = 0 \text{ on }\partial S.
\end{equation}

@@

We define a basis for the dual of $V^2_{p, p_F}(K)$ as 
normal moments on $F\in \text{faces}(\Delta^d)$,
\begin{equation}
   \ell^F_j(v) = (q_j, v\cdot \bn)_F, \quad q_j \in \P_{p_F}(F),
\end{equation}
and on the $\text{interior}(\Delta^d) = K$: 
\begin{align}
   \ell^{K,0}_j(v) &= (\curl\Phi^K_j, v)_{K}, \\
   \ell^{K,1}_j(v) &= (\div\Psi^K_j, \div v)_{K},
\end{align}
where $\{\Phi^K_j\}$ are the $H_0(\curl, S)$ bases constructed in \eqref{eq:hcurl-fdm},
and $\{\div\Psi^K_j\}$ is a basis for $\div \mathbb{Y}_p(K)$,
$\mathbb{Y}_{p}(K) = [\mathbb{P}_p(K)]^d \cap H_0(\div,K)$, such that
\begin{equation} \label{eq:hdiv-fdm}
   (\div\Psi^K_j, \div\Psi^K_i)_{K} = \delta_{ij}, \quad
   (\Psi^K_j, \Psi^K_i)_{K} = \lambda_j\delta_{ij}, \quad
   \Psi^K_j\cdot\bn = 0 \text{ on }\partial K.
\end{equation}

>>>>

We follow the definition of interpolation degrees of freedom from
\cite{demkowicz00} to construct dual bases that promote orthogonality in the
$\Ltwo(\Khat)$ and $H(\mathrm{d}, \Khat)$ inner products.

We denote the space of polynomials with vanishing boundary trace as
$\mathbb{B}_{p}(\mathrm{d}, K) = [\P_{p}(K)]^d \cap H_0(\mathrm{d}, K)$.

@@

Let $\Delta^d$ be the equilateral $d$-simplex.
We define a basis for the dual of $\CG_p$ as 
point evaluations at $V \in \text{vertices}(\Delta^d)$,
\begin{equation}
   \ell^V(v) = v(\bx_V),
\end{equation}
and for each sub-entity $S \in \text{edges}(\Delta^d) \cup \text{faces}(\Delta^d) \cup \text{interior}(\Delta^d)$
we take integral moments of surface gradients, 
\begin{equation}
   \ell^S_j(v) = (\grad_S\phi^S_j, \grad_S v)_{S},
\end{equation}
where $\grad_S$ is the tangential gradient on $S$,
and $\{\phi^S_j\}$ is a basis for $\mathbb{B}_{p}(\grad, S)$, such that
\begin{equation} \label{eq:hgrad-fdm}
   (\grad_S\phi^S_j, \grad_S\phi^S_i)_{S} = \delta_{ij}, \quad
   (\phi^S_j, \phi^S_i)_{S} = \lambda_j\delta_{ij}.
\end{equation}
The eigenbases $\{\phi^S_j\}$ are numerically computed offline and only once 
on the reference interval, triangle, and tetrahedron.

@@

We define a basis for the dual of $V^1_{p, p_E}(K)$ as 
tangential moments along $E\in \text{edges}(\Delta^d)$,
\begin{equation}
   \ell^E_j(v) = (q_j, v\cdot \bt)_E, \quad q_j \in \P_{p_E}(E), 
\end{equation}
and for each sub-entity $S \in \text{faces}(\Delta^d) \cup \text{interior}(\Delta^d)$,
\begin{align}
   \ell^{S,0}_j(v) &= (\grad_S\phi^S_j, v)_{S}, \\
   \ell^{S,1}_j(v) &= (\curl_S\Phi^S_j, \curl_S v)_{S},
\end{align}
where $\curl_S$ is the tangential curl on $S$,
$\{\phi^S_j\}$ are the $H_0(\grad, S)$ bases constructed in \eqref{eq:hgrad-fdm},
and $\{\curl_S\Phi^S_j\}$ is a basis for $\curl_S \mathbb{B}_{p_S}(\curl, S)$
such that
\begin{equation} \label{eq:hcurl-fdm}
   (\curl_S\Phi^S_j, \curl_S\Phi^S_i)_{S} = \delta_{ij}, \quad
   (\Phi^S_j, \Phi^S_i)_{S} = \lambda_j\delta_{ij}, \quad
   \Phi^S_j\times\bn = 0 \text{ on }\partial S.
\end{equation}

@@

We define a basis for the dual of $V^2_{p, p_F}(K)$ as normal moments on $F\in
\text{faces}(\Delta^d)$,
\begin{equation}
   \ell^F_j(v) = (q_j, v\cdot \bn)_F, \quad q_j \in \P_{p_F}(F),
\end{equation}
and on the $\text{interior}(\Delta^d) = K$: 
\begin{align}
   \ell^{K,0}_j(v) &= (\curl\Phi^K_j, v)_{K}, \\
   \ell^{K,1}_j(v) &= (\div\Psi^K_j, \div v)_{K},
\end{align}
where $\{\Phi^K_j\}$ are the $H_0(\curl, S)$ bases constructed in
\eqref{eq:hcurl-fdm}, and $\{\div\Psi^K_j\}$ is a basis for $\div
\mathbb{B}_p(\div, K)$ such that
\begin{equation} \label{eq:hdiv-fdm}
   (\div\Psi^K_j, \div\Psi^K_i)_K = \delta_{ij}, \quad
   (\Psi^K_j, \Psi^K_i)_{K} = \lambda_j\delta_{ij}, \quad
   \Psi^K_j\cdot\bn = 0 \text{ on }\partial K.
\end{equation}
